### 2025-04-18 mixed-models.qmd
20250418 - fix plots
20250418 - figure labels

```{r}
plot(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)

@@

```{r}
plot(
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience,
  sqrt(abs(resid(.))) ~ fitted(.),
  type = c("p","smooth"),
  col.line = 1)
```

@@

```{r}
qqnorm(resid(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience))
qqline(resid(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience))
```

##### Probability–Probability (PP) Plots {#sec-fantasyPointsByAgeExperienceModelsDiagnosticPPPlots}

```{r}
petersenlab::ppPlot(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
```

@@

```{r}
plot(
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience,
  rstudent(.) ~ hatvalues(.))
```

@@

```{r}
performance::check_model(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
```

>>>>

```{r}
#| label: fig-residualPlotMixedModel
#| fig-cap: "Plot of Residuals."
#| fig-alt: "Plot of Residuals."

@@

```{r}
#| label: fig-scaleLocationPlotMixedModel
#| fig-cap: "Scale-Location Plot."
#| fig-alt: "Scale-Location Plot."

plot(
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience,
  sqrt(abs(resid(.))) ~ fitted(.),
  type = c("p","smooth"),
  col.line = 1)
```

@@

```{r}
#| label: fig-qqPlotMixedModel
#| fig-cap: "Quantile–Quantile (QQ) Plot."
#| fig-alt: "Quantile–Quantile (QQ) Plot."

qqnorm(resid(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience))
qqline(resid(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience))
```

##### Probability–Probability (PP) Plot {#sec-fantasyPointsByAgeExperienceModelsDiagnosticPPPlots}

```{r}
#| label: fig-qqPlotMixedModel
#| fig-cap: "Probability–Probability (PP) Plot."
#| fig-alt: "Probability–Probability (PP) Plot."

petersenlab::ppPlot(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
```

@@

```{r}
#| label: fig-residualsVsLeveragePlotMixedModel
#| fig-cap: "Residuals Versus Leverage Plot."
#| fig-alt: "Residuals Versus Leverage Plot."

plot(
  pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience,
  rstudent(.) ~ hatvalues(.))
```

@@

```{r}
#| label: fig-otherDiagnosticPlotsMixedModel
#| fig-cap: "Other Diagnostic Plots."
#| fig-alt: "Other Diagnostic Plots."
#| fig-height: 10

performance::check_model(pointsPerSeason_positionAgeRandomLinearFixedQuadraticSlopesInteractionExperience)
```
